%!TEX root = ../main.tex
%-------------------------------------------------------------------------------
\section{Conclusion}
%-------------------------------------------------------------------------------
So, I hope I made the case that incorporating ambiguity in dynamic discrete choice models is potentially fruitful undertaking. It is a plausible, meaningful, and tractable extension to the standard model under risk.\\\newline
%
The \textbf{final goal} is clear. Fit a more general model of educational choices under ambiguity to the NLSY that then allows to asses the relative importance of competing economic mechanisms and conduct an ex ante evaluation of alternative policy proposals.\\\newline
% 
However, there are a couple of papers that I want to exist to make this a sound extension to the standard model. 

\begin{itemize}
\item I want to work with a graduate students to provide an upgraded recomputation of the results in the original paper.
\item I am working with Stefan Wild from Argonne National Labs to meet the numerical challenges of the standard model with state of the art approaches. 
\item Then we need to assess the performance of all the numerical components for models of ambiguity.
\end{itemize}

These improvements to the standard model provide a sound foundation to tackle the additional challenges posed by studying ambiguity.\\\newline
%
Alright, that is it. Thank you very much for your attention. i very much look forward to any further questions an comments from your side.






\nocite{Iyengar.2005,Maccheroni.2006,Gilboa.1989,Hansen.2007,Eisenhauer.2015b}

\newpage\bibliographystyle{apalike}
\bibliography{../material/literature}
